Really Good Title

### 2019-01-07 documentation/paper.tex
Two-species all vs best

In this scenario \ref{fig:self_adapt_1_self_training_2_oldrun}

\todo{sadly they do not change too often}
\todo{there is still improvement even though it can not be seen in the plots because they improve themselves}

@@

\todo{we got a pretty awesome bot there which gets beaten only by reduced but never trained against it}

>>>>

\todo{too much diversity <<-- what does this mean?}

In this scenario \ref{fig:self_adapt_1_self_training_2_oldrun} can be seen battling for being the better species in the beginning, but then this seems to converge. A quick manual check confirms however, that they are both still actively learning. When left alone to train for 8000 generations (figure \ref{fig:self_adapt1_self_training_2}) we get the best results so far (figure \ref{fig:self_training_2}). The only bot capable of matching this network is the strongest \texttt{reduced} bot, but it never trained against any of the built-in bots directly. (In fact, this network was too strong even for us humans to beat in the game.)

@@
